\documentclass[line,margin]{res} 

\usepackage{hyperref}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Header
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\name{Lucas A. Scharf}
\address{201 E Mumford Dr, Urbana, IL 61801}
\address{540-818-5876 or \href{mailto:lukescharf@clusterbee.net}{lukescharf@clusterbee.net}}

 
\begin{resume}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Summary
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
%\section{SUMMARY} MBA-educated computer systems engineer with operational
%experience on Big Data and High Performance Computing systems.

 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{EDUCATION} {\sl Masters of Business Administration} \\
	University of Illinois at Urbana-Champaign, 2013

	{\sl Bachelors of Science} in Computer Science\\ 
	Virginia Tech, 2001



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{EXPERIENCE}
	{\sl ATS Acoustics} \hfill September 2019 - November 2019 \\
        Full Stack Developer \\

        \begin{itemize}

               \item {\sl Full Stack Developer:} Maintain and extend legacy custom Perl and PHP E-Commerce and ERP applications on a team of 2.

               \item {\sl Devops:} Taught GitHub use, instituted code reviews, and applied the subset of Agile/DevOps methodologies which benefited the team.

               \item {\sl Sysadmin:} Maintain servers, desktops, backups, and other tech resources as-needed.

               \item Laid off because my employer no longer wants to be in the custom software business.
        
        \end{itemize}

	{\sl Full-time Parent} \hfill February 2017 - September 2019 \\
	\begin{itemize}
	
		\item {\sl Primary Caregiver:} Three children, ages 9, 4, and 2.

		\item {\sl Illini Glider Club:} Treasurer.  Oversee finances for 5 club-owned aircraft, worth roughly \$100k in total.  Core member of the leadership team.  Act as Ground Operations Director (organize club activity to ensure smooth and safe flight operations, oversee volunteers, and teach ground-handling of aircraft).  Our team has successfully relocated the club (including all aircraft) from Monticello, IL (2K0) to Danville, IL (KDNV).

		\item {\sl Leal Elementary School:} PTA Secretary.

		\item {\sl Cooperative Nursery School:} Parent volunteer.

	\end{itemize}

	{\sl Oso Technologies \& Scotts Miracle-Gro / PlantLink, Urbana, IL} \hfill February 2016 - February 2017 \\
	VP of Software Engineering \& Sr. Software Engineer \\
	\begin{itemize}
	
		\item {\sl Manage Software Development Effort:} Manage multiple contractors developing multiple interlocking components of the PlantLink Soil Moisture Sensor system (IoT).

		\item {\sl Architecture:} Oversee the system-wide architecture and interfaces between the components of the PlantLink system, including device firmware, backend services, and mobile app.

		\item {\sl Systems Integration \& Testing:} Ensure that the different components of the system work together.

		\item {\sl ZigBee Firmware Development:} Develop major portions of the firmware for the PlantLink Lush Sensor and PlantLink Lush Valve.
		
		\item {\sl Startup:} Small product development startup, geographically distributed team, acquired by Scotts Miracle-Gro.

	\end{itemize}

	{\sl Altiscale, Inc, Palo Alto California (Remote)} \hfill April 2015 - November 2015 \\
	DevOps Engineer / Site Reliability Engineer \\
	\begin{itemize}
		
		\item {\sl Operations Team:} Operate Hadoop-based cloud service for commercial customers.  Fix service outages and address customer requests.
		
		\item {\sl Startup:} Series B Startup, with an Agile+DevOps environment, and a globally distributed team.
	
	\end{itemize}	

	{\sl Yahoo, Inc, Champaign Illinois} \hfill July 2012 - March 2015 \\
	Computer Systems Engineer, Senior \\
	\begin{itemize}

		\item {\sl Data Highway Petascale Big Data Ingestion System - Oncall Systems Engineer \& DevOps:} \\
		The data ingestion system collects web activity logs from
		20,000+ active webservers distributed across Yahoo'۪s global
		network, and provides data to a variety of Hadoop and  Apache Storm consumers within Yahoo.
		\begin{itemize}

			\item {\sl DevOps:} Worked closely with an
			Agile-influenced software development team to provide
			operational support \& troubleshooting.  Used Chef in
			production.

			\item {\sl Project Lifecycle:} Provided an operational perspective during the architecture, design, and development stages.
			Performed production bring-up of the initial service,
			and maintained the system during its growth to full scale
			operation.  Also, maintained the previous data
			ingestion system from production through decommissioning.

		\end{itemize}	

		\item {\sl Advertising Data Analysis Pipelines - Oncall Systems Engineer:} \\
		Performed oncall troubleshooting for Big Data analysis
		applications in the revenue path running on Hadoop.

	\end{itemize}

	{\sl University of Illinois, National Center for Supercomputing Applications} \hfill May 2008 - July 2012 \\
	Computer Systems Engineer \\
	\begin{itemize}

		\item {\sl Private Sector Program Team:} Represent NCSA to
		external partners, and provide HPC computer systems engineering
		support to projects performed with external partners.
		Participated in I-Forge cluster build effort.  Represented NCSA
		during on-site consulting.

		\item {\sl Blue Water Systems Administration Team:} Provided
		supporting infrastructure and some general systems
		administration to Blue Waters HPC cluster build effort.

		\item {\sl Persistent Infrastructure Team:} Provided support
		for Grid Services applications (GLOBUS), as well as an
		automated Certificate Authority (MyProxy) and Kerberos
		authentication infrastructure.

	\end{itemize}

	{\sl Virginia Tech, Advanced Research Computing} \hfill July 2006 - May 2008 \\
	HPC Systems Administrator, Advanced Research Computing \\
	\begin{itemize}

		\item Primary systems administrator for System X, a 1200-node
		12 teraflop Mac OS X based supercomputer.
	
		\item Implemented a storage upgrades and improved system
		reliability.

		\item Represented Virginia Tech Advanced Research Computing at
		Supercomputing on tours and across campus.  Spoke in front of a
		100+ member audience at the QLogic Fusion conference in 2007.

	\end{itemize}

	{\sl Virginia Tech, Department of Aerospace and Ocean Engineering} \hfill November 2003 - July 2006 \\
	Systems Administrator \\
	\begin{itemize}

		\item Provided deskside IT support for a heterogeneous network
		of 120+ Windows / Linux / Solaris / IRIX workstations for use
		by faculty, staff, and students.

		\item Provided IT support for a wind tunnels, full-motion
		flight simulator, the satellite systems simulation lab, and a
		variety of other research labs.

		\item Provided computational environments suitable for running
		a variety of engineering applications ranging from AutoCad to
		Abaqus, Ansys, LS-DYNA, Fluent, Matlab, Tecplot, and related
		software.  Managed the departmental website and
		rewrote/refactored the department's homebrew CMS using the LAMP
		stack.
			
		\item HPC Deployment: Acted as the technical coordinator for
		the installation and maintenance of a 38-rack 512-CPU SGI
		Origin 3800 shared memory supercomputer.

	\end{itemize}

	{\sl Virginia Tech, Department of Entomology} \hfill June 2002 - November 2003
	DBA for Slow The Spread gypsy moth population survey \\
	\begin{itemize}

		\item Administered a Oracle database server.  The database fed
		in to a pest control analysis system based on ESRI ArcView and
		later ArcGIS.

		\item Assisted in the development of a mobile and
		geographically-aware data-collection application using WinCE
		and GPS.  Traveled to nine states to train end-users on the use
		of the application.

	\end{itemize}

	{\sl Various Part Time Positions} \hfill 1993 - 2002
	\begin{itemize}

		\item {\sl Virginia Tech Configurable Computing Lab, 1998 - 2001:} \\
		Systems Administrator for a 16-node Linux/Windows HPC cluster
		with a Myrinet interconnect and FPGA-based computational
		accelerators.  Supported a variety of FPGA development
		toolchains used in an academic research setting.

		\item {\sl Virginia Tech Scientific Visualization Lab, 2002:} \\
		Assisted in the maintenance of computer systems used to drive
		the VT CAVE (4-wall immersive virtual reality system), as well
		as immersive head mounted displays (HMDs).

		\item {\sl Intransa Inc, 2001:} \\
		Summer internship with a startup company.  Assisted in hardware
		development of FPGA-based bulk disk storage system.

		\item {\sl Shenandoah Technology Systems, 1993 - 1997:} \\
		Computer technician for my family's computer shop during high
		school.  Provided PC sales \& service to small businesses,
		local government, and individual customers throughout
		Shenandoah County Virginia.

	\end{itemize}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Supplementary Page
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage
%\section{Skills}
%	{\sl Prepared to Discuss: } \\
%	\begin{itemize}
%
%		\item {\sl Management:} MBA Topics, organizational behavior,
%		Agile, Kanban, etc.
%
%		\item {\sl Big Data:} Big Data concepts, administration of
%		large/distributed systems, failover \& resiliency, petascale
%		data ingestion, streaming data processing, NoSQL databases,
%		Hadoop.
%
%		\item {\sl HPC:} High Performance Computing, Supercomputing,
%		Parallel Computing, MPI, Infiniband, Myrinet, Technical
%		Computing, Computing for Engineering and Science, Computational
%		Modeling \& Simulation, Storage.
%
%		\item {\sl Systems Administration Topics:} Linux/Unix, Windows,
%		Enterprise Directory Services, Active Directory, LDAP,
%		Kerberos, sendmail, RAID Storage, ZFS, courier, SMTP, IMAP,
%		Shell Scripting, Chef.
%
%		\item {\sl Software Development:} Ruby, Perl, PHP, bash, scripting
%		languages, C/C++, Agile, Kanban, and Free/Open Source Software.
%
%		\item {\sl Web Services Administration:} Linux Apache MySQL PHP
%		(LAMP), and related.
%
%		\item {\sl Database Administration:} SQL, MySQL, Oracle,
%		CouchDB.
%
%	\end{itemize}


%\section{TECHNICAL HOBBIES}
%	{\sl Champaign-Urbana Community Fab Lab Core Volunteer \hfill 2010 - 2012} \\
%	The Champaign-Urbana Community Fab Lab is a technical crafting
%	community which provides public access to CNC machine tools such as a
%	laser cutter, 3D   printers, 3D routers, and an electronics lab.  The
%	culture of this group   emphasis is on peer-to-peer teaching.  Members
%	also use and teach more traditional crafting skills such as sewing,
%	woodworking, and metalworking.


\end{resume}


\end{document}







